paper2_resistance_mechanisms_mixtures

### 2016-12-14 inst/documents/paper2/paper2_resistance_mechanisms_mixtures.Rmd
tweak text, add to legend

## ANDY TO DO
1. add to intro including about about results in levick et al.
1. work out what's going on with exposure ... why does increasing exposure have a greater effect on mixture than sequential ? 
1. explain resistance-restoration and its relation to selection coefficient
1. expand discussion to include relevance to real world 
1. in discussion address potential criticism that these results are just for a limited region of paramter space (a. point to Levick et al. that explored more of space, b. point to UI that allows readers to explore spce for themselves and identify whether there are places where this does not hold).
1. ? briefly refer to linkage disequilibrium and say we are investigating.

1. can I develop explanatory diagrams to describe the input parameters ?
1. mention generation time of 1 month
1. mention other potential effects e.g. differential exposure of M&F, sex linkage, ...
1. add to discussion about relevance of these mechanisms in the field e.g. exposure can be reduced if either insecticide has a repellant effect, which can be set in formulation. (Birget & Koella 2015 mention this not for resistance but for ITNs with repellancy requiring higher coverage for elimination)

@@

Parameter  | Description
------------------- | -------------------------------------------------------
1. Effectiveness | proportion of exposed insects with both susceptible alleles that are killed by the insecticide
2. Exposure | proportion of the insect population that are exposed to the insecticide
3. Dominance | dominance of the resistance allele relative to the susceptible allele
4. Resistance restoration  | ability of resistance to restore fitness in the presence of the insecticide
5. Frequency  | frequency of resistance alleles within the population

@@

**Ian, Matt this is still the bit I can't quite explain. Any suggestions ?**

@@

legend( 'bottom', legend=c("insecticide1 alone   ", "insecticide1 in mix   ", "insecticide2 alone   ", "insecticide2 in mix   "), col=c("red","red","blue","blue"), lty=c(2,1,2,1), pch=c(NA,NA,NA,NA), bty="n", cex=0.7, horiz =TRUE )

>>>>

## ANDY TO DO
1. should I include male exposure prop ?
1. add to intro including about about results in levick et al.
1. work out what's going on with exposure ... why does increasing exposure have a greater effect on mixture than sequential ? 
1. explain resistance-restoration and its relation to selection coefficient
1. expand discussion to include relevance to real world 
1. in discussion address potential criticism that these results are just for a limited region of paramter space (a. point to Levick et al. that explored more of space, b. point to UI that allows readers to explore spce for themselves and identify whether there are places where this does not hold).
1. ? briefly refer to linkage disequilibrium and say we are investigating.

1. can I develop explanatory diagrams to describe the input parameters ?
1. mention other potential effects e.g. differential exposure of M&F, sex linkage, ...
1. add to discussion about relevance of these mechanisms in the field e.g. exposure can be reduced if either insecticide has a repellant effect, which can be set in formulation. (Birget & Koella 2015 mention this not for resistance but for ITNs with repellancy requiring higher coverage for elimination)
1. mention in discussion that repellency would lead to decrease in exposure

@@

Parameter  | Description
------------------- | -------------------------------------------------------
1. Effectiveness | proportion of susceptible (SS) insects killed by exposure to insecticide
2. Exposure | proportion of insects exposed to the insecticide
3. Dominance | resistance of an insect with only 1 resistance allele (SR)
4. Resistance restoration  | ability of resistance (RR) to restore fitness when insect exposed to the insecticide
5. Frequency  | frequency of resistance alleles within the population

@@

**work on explaining this without getting too carried away**

@@

# legend( 'bottom', legend=c("insecticide1 alone   ", "insecticide1 in mix   ", "insecticide2 alone   ", "insecticide2 in mix   "), col=c("red","red","blue","blue"), lty=c(2,1,2,1), pch=c(NA,NA,NA,NA), bty="n", cex=0.7, horiz =TRUE )

#add for when insecticides same
legend( 'bottom', legend=c("insecticide1 alone   ", "insecticide2 alone   ", "insecticide1 in mix   ", "insecticide2 in mix   ", "insecticides1&2 in mix   "), col=c("red","blue","red","blue","purple"), lty=c(2,2,1,1,1), pch=c(NA,NA,NA,NA,NA), bty="n", cex=0.7, horiz =TRUE )
